### 2020-01-30 ChapterStatisticalAnalysis/ChapterStatisticalAnalysis.tex
Preliminaries ready

\chapter{Statistical Analysis}\label{chap:StatisticalAnalysis}

\begin{quote}
\emph{The results of this chapter ...}\vfill{}
\end{quote}

\section{Introduction}

@@

\section{Statistical analysis}

For an overdetermined system of linear equations, the least-squares (LS) solution is given by
\begin{equation} \widehat{\mathbf{x}} = \widetilde{\mathbf{K}}^\dagger \widetilde{\mathbf{y}} = ( \widetilde{\mathbf{K}}^\top \widetilde{\mathbf{K}} )^{-1} \widetilde{\mathbf{K}}^\top \widetilde{\mathbf{y}} , \label{eqn:xhat} \end{equation}
where $\widetilde{\mathbf{K}}^\dagger$ is the pseudo-inverse of $\widetilde{\mathbf{K}}$.
The objective of the statistical analysis is to obtain the bias and the covariance of the solution $\widehat{\mathbf{x}}$.
The bias and the covariance are computed using the mathematical expectation operator $\mathbb{E}\{\cdot\}$.
First we substitute (\ref{eqn:y0plusnoise}) and (\ref{eqn:K0plusnoise}) in (\ref{eqn:xhat}) obtaining
\begin{equation*} \widehat{\mathbf{x}} = \left( (\mathbf{K}+\mathbf{E})^\top (\mathbf{K}+\mathbf{E})  \right)^{-1} (\mathbf{K}+\mathbf{E})^\top (\mathbf{y}+\bm{\epsilon}), \end{equation*} 
which is equivalent to
\begin{equation} \widehat{\mathbf{x}} = \left( \mathbf{I} + \mathbf{M} \right)^{-1} \mathbf{Q}^{-1} (\mathbf{K}+\mathbf{E})^\top (\mathbf{y}+\bm{\epsilon}), \label{eqn:1steq} \end{equation} 
where 
\begin{equation} \mathbf{Q} = \mathbf{K}^\top \mathbf{K}, \quad \text{and} \quad \mathbf{M} = \mathbf{Q}^{-1} ( \mathbf{K}^\top \mathbf{E} + \mathbf{E}^\top \mathbf{K} + \mathbf{E}^\top \mathbf{E} ). \end{equation} 
Applying a second-order Taylor expansion of the inverse matrix
\begin{equation} (\mathbf{I} + \mathbf{M})^{-1} \approx \mathbf{I} - \mathbf{M} + \mathbf{M}^2, \label{eqn:TseriesExp} \end{equation} 
that is valid when the SNR is sufficiently high, and therefore $\mathbf{E}$ and $\mathbf{M}$ are small, satisfying the constraint on the spectral radius $\| \mathbf{M} \| < 1$. 
The neglected term in the Taylor series expansion is of the order $O(\Vert M \Vert^3)$.
We can express the estimate as
\begin{equation} \widehat{\mathbf{x}} \approx \left( \mathbf{I} - \mathbf{M} + \mathbf{M}^2 \right) \mathbf{Q}^{-1} (\mathbf{K}+\mathbf{E})^\top (\mathbf{y}+\bm{\epsilon}). \label{eqn:xhatexp} \end{equation}

@@

This subsection describes the statistics of a structured EIV problem with correlation between the perturbations of the regression matrix and the regressor. 
The structured EIV problem is given by the step input estimation method (\ref{eqn:min_ls}).
The correlation is a consequence of the construction of the block-Hankel matrix in the regression matrix $\widetilde{\mathbf{K}}$ with the first difference of the elements in the regressor $\widetilde{\mathbf{y}}$.

@@

The minimization problem (\ref{eqn:min_ls}) is equivalent to a structured EIV problem that can be expressed as a linear in the measurements problem \citep{Pintelon12Book}
\begin{equation} e (\widehat{\mathbf{x}}, \widetilde{\mathbf{z}}) = \mathbf{M}_1( \widehat{\mathbf{x}} ) \ \widetilde{\mathbf{z}} = \begin{bmatrix} \mathbf{I}_{T-n} & - \widehat{\mathbf{x}}^T \otimes \mathbf{I}_{T-n} \end{bmatrix} \begin{bmatrix} \widetilde{\mathbf{y}} \\ \mathrm{vec} ( \widetilde{\mathbf{K}} ) \end{bmatrix} = 0 . \label{eqn:M1vecyK} \end{equation}
where $\widetilde{\mathbf{z}} = \mathbf{z} + \epsilon_{\mathbf{z}}$.
The CRB requires that the true model $\mathbf{M}_1( \mathbf{x} ) \ \mathbf{z} = 0$ exists.
Under the assumption of the measurement perturbation $\epsilon_{\mathbf{z}}$ being normally distributed with covariance matrix $\mathbf{C}_{\mathbf{z}}$, the loglikelihood function of the structured EIV problem is
\begin{equation} \ln{ l(\widetilde{\mathbf{z}}, \widehat{\mathbf{z}}, \widehat{\mathbf{x}}) } = - \frac{1}{2} \left( \widetilde{\mathbf{z}} - \widehat{\mathbf{z}} \right)^\top \mathbf{C}_{\mathbf{z}}^{-1} \left( \widetilde{\mathbf{z}} - \widehat{\mathbf{z}} \right) + \mathrm{constant}, \end{equation}
where $\widehat{\mathbf{z}}$ are parameters of the measurements $\widetilde{\mathbf{z}}$ that have to be estimated and satisfy $\mathbf{M}_1( \widehat{\mathbf{x}} ) \ \widehat{\mathbf{z}} = 0$.
The size of the Fisher information matrix $\mathbf{Fi}(\mathbf{x}, \mathbf{z})$ depends on the number of unknowns in $\widehat{\mathbf{z}}$ and grows with the sample size.
Moreover, in Chapter 19 of \citep{Pintelon12Book} it is shown that the Fisher information matrix $\mathbf{Fi}(\mathbf{x})$ can be obtained from $\mathbf{Fi}(\mathbf{x}, \mathbf{z})$ after doing inversion by parts, giving
\begin{equation} \mathbf{Fi}(\mathbf{x}) = \left( \frac{\partial e (\widehat{\mathbf{x}}, \mathbf{z}) }{\partial \mathbf{x} } \right)^\top \left( \mathbf{M}_1( \mathbf{x} ) \ \mathbf{C}_{\mathbf{z}} \ \mathbf{M}_1^\top( \mathbf{x} ) \right)^{-1} \left( \frac{\partial e (\widehat{\mathbf{x}}, \mathbf{z}) }{\partial \mathbf{x} } \right) 
 , \label{eqn:FIM} \end{equation} 
where the partial derivatives are evaluated at the true values $\mathbf{x}$, and the covariance matrix of the measurements is
\begin{equation} \mathbf{C}_{\mathbf{z}} = \sigma_{\epsilon}^2 \begin{bmatrix} \mathbf{I}_{T-n} & \mathbf{0}_{T-n} & \mathbf{D}_{T-n \times T-n}^{1,n} & \mathbf{D}_{T-n \times T-n}^{1,n-1} & \cdots & \mathbf{D}_{T-n \times T-n}^{1,1} \\ \mathbf{0}_{T-n} & \mathbf{0}_{T-n} & \mathbf{0}_{T-n} & \mathbf{0}_{T-n} & \cdots & \mathbf{0}_{T-n} \\ \left( \mathbf{D}_{T-n \times T-n}^{1,n} \right)^\top & \mathbf{0}_{T-n} & \mathbf{D}_{T-n \times T-n}^{2,1} & \mathbf{D}_{T-n \times T-n}^{2,0} & \cdots & \mathbf{D}_{T-n \times T-n}^{2,2-n} \\ \left( \mathbf{D}_{T-n \times T-n}^{1,n-1} \right)^\top & \mathbf{0}_{T-n} & \mathbf{D}_{T-n \times T-n}^{2,2} & \mathbf{D}_{T-n \times T-n}^{2,1} & \cdots & \mathbf{D}_{T-n \times T-n}^{2,3-n} \\ \vdots & \vdots & \vdots & \vdots & & \vdots \\ \left( \mathbf{D}_{T-n \times T-n}^{1,1} \right)^\top & \mathbf{0}_{T-n} & \mathbf{D}_{T-n \times T-n}^{2,n} & \mathbf{D}_{T-n \times T-n}^{2,n-1} & \cdots & \mathbf{D}_{T-n \times T-n}^{2,1} \end{bmatrix} .
 \label{eqn:Cz} \end{equation}

The Cram\'er-Rao lower bound for an biased estimator of the minimization problem (\ref{eqn:min_ls}) is given by
\begin{equation} \mathrm{CRB}_{\mathrm{b}}(\mathbf{x}) = \left( \mathbf{I}_{n+1} + \frac{\partial \mathbf{b} \left( \widehat{\mathbf{x}} \right) }{\partial \mathbf{x} } \right)^\top \ \mathbf{Fi}^{-1}(\mathbf{x}) \ \left( \mathbf{I}_{n+1} + \frac{\partial \mathbf{b} \left( \widehat{\mathbf{x}} \right) }{\partial \mathbf{x} } \right), \label{eqn:CRB_EIV} \end{equation} 
and for an unbiased estimator it is $\mathrm{CRB}_{\mathrm{ub}}(\mathbf{x}) = \mathbf{Fi}^{-1}(\mathbf{x})$.

@@

Two Monte Carlo (MC) simulation studies were conducted to test the obtained bias and variance formulas.
One MC simulation was devoted to the unstructured EIV problem and the other to the structured EIV problem that corresponds to the step input estimation method (\ref{eqn:min_ls}).
The MC simulations performed $N_{MC} = 10^6$ runs of the LS estimator with different realizations of the perturbation $[\begin{matrix} \mathbf{E} & \bm{\epsilon}] \end{matrix}$.
In the structured EIV problem the perturbation $\mathbf{E}$ is correlated with $\bm{\epsilon}$.
The perturbations variance was selected to have a signal-to-noise ratio (SNR) in the interval [30 dB, 80 dB], according to 
\begin{equation} \mathrm{SNR} = 20 \log_{10}{ \dfrac{ \sqrt{ \dfrac{1}{T} \sum\limits_{t=1}^{T}{ y(t)^2 } } }{ \sigma_{ \bm{\epsilon}}} } . \end{equation} 
For high enough SNR, the constraint $\| \mathbf{M} \| < 1$ is valid and the Taylor series expansion  (\ref{eqn:TseriesExp}) holds. 
In this case, the derived expressions predict the LS estimate bias and variance.
Thus, it is relevant to monitor the evolution of the largest $\mathbf{M}$ eigenvalue to detect the lower limit of the SNR  that allows the validity of the predictions.

@@

The MC simulation of the structured EIV problem (\ref{eqn:min_ls}) solution was conducted processing $T = 200$ samples of the transient response $\widetilde{\mathbf{y}}$ generated by a linear time invariant system of order $n = 2$, after a step input excitation with $u = 1 \ \mathrm{units}$, where the units represent any physical quantity. 
The processed step response is shown in Figure \ref{fig:y}.
The steady state response of the system is reached after 400 samples because from there on the relative error between the instantaneous values of the transient response and the steady-state response value is smaller than 2\%.
Processing 200 samples ensures that the step input estimation is computed from transient data only.
%In the following results we focus our interest in the first element of the estimate $\widehat{\mathbf{x}}_{\left[1\right]}$, where the step input level estimate $\widehat{u}$ is located.

>>>>

\chapter{Statistical Analysis} \label{chap:StatisticalAnalysis}

\begin{quote}
\emph{The results of this chapter were published in Quintana Carapia, G., Markovsky, I. Pintelon, R., Csurcsia, P.Z., and Verbeke, D., "Bias and covariance of the least squares estimate in a structured errors-in-variables problem", Computational Statistics & Data Analysis journal, Vol. 144, 2020, ISSN 0167-9473, doi:10.1016/j.csda.2019.106893. \nocite{QuintanaCSDA} }\vfill{}
\end{quote}

\vfill{}

%\section{Introduction}

@@

\section{Statistical analysis of the data-driven step input estimation method}

For an overdetermined system of linear equations, constructed by the data-driven step input estimation method (\ref{eqn:min_seiv}), the least-squares (LS) solution is given by
\begin{equation} \widehat{\mathbf{x}} = \widetilde{\mathbf{K}}^\dagger \widetilde{\mathbf{y}} = ( \widetilde{\mathbf{K}}^\top \widetilde{\mathbf{K}} )^{-1} \widetilde{\mathbf{K}}^\top \widetilde{\mathbf{y}} , \label{eqn:xhat} \end{equation}
where $\widetilde{\mathbf{K}}^\dagger$ is the pseudo-inverse of $\widetilde{\mathbf{K}}$.
The objective of the statistical analysis is to obtain the bias and the covariance of the solution $\widehat{\mathbf{x}}$ to the structured and correlated EIV problem (\ref{eqn:ddsiemnd}).
The bias and the covariance are computed using the mathematical expectation operator $\mathbb{E}\{\cdot\}$.
First we substitute the expressions (\ref{eqn:y0plusnoise}) and (\ref{eqn:K0plusnoise}) in Equation (\ref{eqn:xhat}) to obtain
\begin{equation*} \widehat{\mathbf{x}} = \left( (\mathbf{K}+\mathbf{E})^\top (\mathbf{K}+\mathbf{E})  \right)^{-1} (\mathbf{K}+\mathbf{E})^\top (\mathbf{y}+\bm{\epsilon}), \end{equation*} 
which is equivalent to
\begin{equation} \widehat{\mathbf{x}} = \left( \mathbf{I} + \mathbf{M} \right)^{-1} \mathbf{Q}^{-1} (\mathbf{K}+\mathbf{E})^\top (\mathbf{y}+\bm{\epsilon}), \label{eqn:1steq} \end{equation} 
where 
\begin{equation} \mathbf{Q} = \mathbf{K}^\top \mathbf{K}, \quad \text{and} \quad \mathbf{M} = \mathbf{Q}^{-1} ( \mathbf{K}^\top \mathbf{E} + \mathbf{E}^\top \mathbf{K} + \mathbf{E}^\top \mathbf{E} ). \end{equation} 
Applying a second-order Taylor expansion of the inverse matrix
\begin{equation} (\mathbf{I} + \mathbf{M})^{-1} \approx \mathbf{I} - \mathbf{M} + \mathbf{M}^2, \label{eqn:TseriesExp} \end{equation} 
that is valid when the SNR is sufficiently high, and therefore $\mathbf{E}$ and $\mathbf{M}$ are small, satisfying the constraint on the spectral radius $\| \mathbf{M} \| < 1$. 
The neglected term in the Taylor series expansion is of the order $O(\Vert M \Vert^3)$.
We can express the estimate as
\begin{equation} \widehat{\mathbf{x}} \approx \left( \mathbf{I} - \mathbf{M} + \mathbf{M}^2 \right) \mathbf{Q}^{-1} (\mathbf{K}+\mathbf{E})^\top (\mathbf{y}+\bm{\epsilon}). \label{eqn:xhatexp} \end{equation}

@@

This subsection describes the statistics of a structured EIV problem with correlation between the perturbations of the regression matrix and the regressor. 
The structured EIV problem is given by the step input estimation method (\ref{eqn:min_seiv}).
The correlation is a consequence of the construction of the block-Hankel matrix in the regression matrix $\widetilde{\mathbf{K}}$ with the first difference of the elements in the regressor $\widetilde{\mathbf{y}}$.

@@

The minimization problem (\ref{eqn:min_seiv}) is a structured EIV problem that can be expressed as a linear in the measurements problem \citep{Pintelon12Book}
\begin{equation} e (\widehat{\mathbf{x}}, \widetilde{\mathbf{z}}) = \mathbf{M}_1( \widehat{\mathbf{x}} ) \ \widetilde{\mathbf{z}} = \begin{bmatrix} \mathbf{I}_{T-n} & - \widehat{\mathbf{x}}^T \otimes \mathbf{I}_{T-n} \end{bmatrix} \begin{bmatrix} \widetilde{\mathbf{y}} \\ \mathrm{vec} ( \widetilde{\mathbf{K}} ) \end{bmatrix} = 0 . \label{eqn:M1vecyK} \end{equation}
where $\widetilde{\mathbf{z}} = \mathbf{z} + \epsilon_{\mathbf{z}}$.
The CRB requires that the true model $\mathbf{M}_1( \mathbf{x} ) \ \mathbf{z} = 0$ exists.
Under the assumption of the measurement perturbation $\epsilon_{\mathbf{z}}$ being normally distributed with covariance matrix $\mathbf{C}_{\mathbf{z}}$, the loglikelihood function of the structured EIV problem is
\begin{equation} \ln{ l(\widetilde{\mathbf{z}}, \widehat{\mathbf{z}}, \widehat{\mathbf{x}}) } = - \frac{1}{2} \left( \widetilde{\mathbf{z}} - \widehat{\mathbf{z}} \right)^\top \mathbf{C}_{\mathbf{z}}^{-1} \left( \widetilde{\mathbf{z}} - \widehat{\mathbf{z}} \right) + \mathrm{constant}, \end{equation}
where $\widehat{\mathbf{z}}$ are parameters of the measurements $\widetilde{\mathbf{z}}$ that have to be estimated and satisfy $\mathbf{M}_1( \widehat{\mathbf{x}} ) \ \widehat{\mathbf{z}} = 0$.
The size of the Fisher information matrix $\mathbf{Fi}(\mathbf{x}, \mathbf{z})$ depends on the number of unknowns in $\widehat{\mathbf{z}}$ and grows with the sample size.
Moreover, in Chapter 19 of \citep{Pintelon12Book} it is shown that the Fisher information matrix $\mathbf{Fi}(\mathbf{x})$ can be obtained from $\mathbf{Fi}(\mathbf{x}, \mathbf{z})$ after doing inversion by parts, giving
\begin{equation} \mathbf{Fi}(\mathbf{x}) = \left( \frac{\partial e (\widehat{\mathbf{x}}, \mathbf{z}) }{\partial \mathbf{x} } \right)^\top \left( \mathbf{M}_1( \mathbf{x} ) \ \mathbf{C}_{\mathbf{z}} \ \mathbf{M}_1^\top( \mathbf{x} ) \right)^{-1} \left( \frac{\partial e (\widehat{\mathbf{x}}, \mathbf{z}) }{\partial \mathbf{x} } \right) 
 , \label{eqn:FIM} \end{equation} 
where the partial derivatives are evaluated at the true values $\mathbf{x}$, and the covariance matrix of the measurements is
\begin{equation} \mathbf{C}_{\mathbf{z}} = \sigma_{\epsilon}^2 \begin{bmatrix} \mathbf{I}_{T-n} & \mathbf{0}_{T-n} & \mathbf{D}_{T-n \times T-n}^{1,n} & \mathbf{D}_{T-n \times T-n}^{1,n-1} & \cdots & \mathbf{D}_{T-n \times T-n}^{1,1} \\ \mathbf{0}_{T-n} & \mathbf{0}_{T-n} & \mathbf{0}_{T-n} & \mathbf{0}_{T-n} & \cdots & \mathbf{0}_{T-n} \\ \left( \mathbf{D}_{T-n \times T-n}^{1,n} \right)^\top & \mathbf{0}_{T-n} & \mathbf{D}_{T-n \times T-n}^{2,1} & \mathbf{D}_{T-n \times T-n}^{2,0} & \cdots & \mathbf{D}_{T-n \times T-n}^{2,2-n} \\ \left( \mathbf{D}_{T-n \times T-n}^{1,n-1} \right)^\top & \mathbf{0}_{T-n} & \mathbf{D}_{T-n \times T-n}^{2,2} & \mathbf{D}_{T-n \times T-n}^{2,1} & \cdots & \mathbf{D}_{T-n \times T-n}^{2,3-n} \\ \vdots & \vdots & \vdots & \vdots & & \vdots \\ \left( \mathbf{D}_{T-n \times T-n}^{1,1} \right)^\top & \mathbf{0}_{T-n} & \mathbf{D}_{T-n \times T-n}^{2,n} & \mathbf{D}_{T-n \times T-n}^{2,n-1} & \cdots & \mathbf{D}_{T-n \times T-n}^{2,1} \end{bmatrix} .
 \label{eqn:Cz} \end{equation}

The Cram\'er-Rao lower bound for an biased estimator of the minimization problem (\ref{eqn:min_seiv}) is given by
\begin{equation} \mathrm{CRB}_{\mathrm{b}}(\mathbf{x}) = \left( \mathbf{I}_{n+1} + \frac{\partial \mathbf{b} \left( \widehat{\mathbf{x}} \right) }{\partial \mathbf{x} } \right)^\top \ \mathbf{Fi}^{-1}(\mathbf{x}) \ \left( \mathbf{I}_{n+1} + \frac{\partial \mathbf{b} \left( \widehat{\mathbf{x}} \right) }{\partial \mathbf{x} } \right), \label{eqn:CRB_EIV} \end{equation} 
and for an unbiased estimator it is $\mathrm{CRB}_{\mathrm{ub}}(\mathbf{x}) = \mathbf{Fi}^{-1}(\mathbf{x})$.

@@

Two Monte Carlo (MC) simulation studies were conducted to test the obtained bias and variance formulas.
One MC simulation was devoted to the unstructured EIV problem and the other to the structured EIV problem that corresponds to the step input estimation method (\ref{eqn:min_seiv}).
The MC simulations performed $N_{MC} = 10^6$ runs of the LS estimator with different realizations of the perturbation $[\begin{matrix} \mathbf{E} & \bm{\epsilon}] \end{matrix}$.
In the structured EIV problem the perturbation $\mathbf{E}$ is correlated with $\bm{\epsilon}$.
The perturbations variance was selected to have a signal-to-noise ratio (SNR) in the interval [30 dB, 80 dB], according to 
\begin{equation} \mathrm{SNR} = 20 \log_{10}{ \dfrac{ \sqrt{ \dfrac{1}{T} \sum\limits_{t=1}^{T}{ y(t)^2 } } }{ \sigma_{ \bm{\epsilon}}} } . \end{equation} 
For high enough SNR, the constraint $\| \mathbf{M} \| < 1$ is valid and the Taylor series expansion  (\ref{eqn:TseriesExp}) holds. 
In this case, the derived expressions predict the LS estimate bias and variance.
Thus, it is relevant to monitor the evolution of the largest $\mathbf{M}$ eigenvalue to detect the lower limit of the SNR  that allows the validity of the predictions.

@@

The MC simulation of the structured EIV problem (\ref{eqn:ddsiemnd}) solution was conducted processing $T = 200$ samples of the transient response $\widetilde{\mathbf{y}}$ generated by a linear time invariant system of order $n = 2$, after a step input excitation with $u = 1 \ \mathrm{units}$, where the units represent any physical quantity. 
The processed step response is shown in Figure \ref{fig:y}.
The steady state response of the system is reached after 400 samples because from there on the relative error between the instantaneous values of the transient response and the steady-state response value is smaller than 2\%.
Processing 200 samples ensures that the step input estimation is computed from transient data only.
%In the following results we focus our interest in the first element of the estimate $\widehat{\mathbf{x}}_{\left[1\right]}$, where the step input level estimate $\widehat{u}$ is located.

### 2020-01-30 Gus-thesis.tex
Preliminaries ready

%%
%% This code was generated from the thesis template of Adam Cooman--Evi Van Nechel.
%% It has been adapted slightly by Gustavo Quintana.
%% Compile with: pdflatex --shell-escape -synctex=1 -interaction=nonstopmode Gus-thesis.tex 
%%
\documentclass[english, british, BCOR=5mm, DIV=12, fontsize=10pt]{scrbook}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[paperwidth=17cm, paperheight=24cm]{geometry}
\geometry{verbose, tmargin=2.5cm, bmargin=3cm, lmargin=2.5cm, rmargin=2cm}
\setcounter{secnumdepth}{2}
\setcounter{tocdepth}{2}
\setlength{\parskip}{\medskipamount}
\setlength{\parindent}{0pt}
\synctex=-1
\usepackage{color}
\definecolor{note_fontcolor}{rgb}{0.800781, 0.800781, 0.800781}
\usepackage{amsmath, amssymb, amsthm, amsbsy, array, babel, booktabs, bm, float, graphicx, mathdots, mathptmx, mathtools, newproof, textcomp, times, units, verbatim}
\usepackage[unicode=true,pdfusetitle, bookmarks=true, bookmarksnumbered=false, bookmarksopen=false, breaklinks=true,pdfborder={0 0 0}, pdfborderstyle={}, backref=false, colorlinks=false] {hyperref}
\usepackage[outdir=./]{epstopdf}
\usepackage{tikz, circuitikz}
\usetikzlibrary{shapes,arrows,calc,patterns,decorations.pathmorphing,decorations.markings,positioning}

@@

>>>>

%%
%% This code was generated from the thesis template of Adam Cooman--Evi Van Nechel.
%% It has been adapted slightly by Gustavo Quintana.
%% Compile with: pdflatex --shell-escape -synctex=1 -interaction=nonstopmode Gus-thesis.tex 
%%
\documentclass[english, british, BCOR=5mm, DIV=12, fontsize=10pt]{scrbook}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[paperwidth=17cm, paperheight=24cm]{geometry} % \usepackage[hmargin=1.5cm, textheight=25cm]{geometry}
\geometry{verbose, tmargin=2.5cm, bmargin=3cm, lmargin=2.5cm, rmargin=2cm}
\setcounter{secnumdepth}{2}
\setcounter{tocdepth}{2}
\setlength{\parskip}{\medskipamount}
\setlength{\parindent}{0pt}
\synctex=-1
\usepackage{color}
\definecolor{note_fontcolor}{rgb}{0.800781, 0.800781, 0.800781}
\usepackage{amsfonts, amsmath, amssymb, amsthm, amsbsy, array, babel, booktabs, bm, float, graphicx, lineno, mathdots, mathptmx, mathtools, newproof, pgf, subcaption, textcomp, times, units, verbatim, xcolor}
\usepackage[unicode=true, pdfusetitle, bookmarks=true, bookmarksnumbered=false, bookmarksopen=false, breaklinks=true, pdfborder={0 0 0}, pdfborderstyle={}, backref=false, colorlinks=false]{hyperref}
\usepackage[outdir=./]{epstopdf}
\usepackage{tikz, circuitikz}
\usetikzlibrary{shapes, arrows, calc, patterns, decorations.pathmorphing, decorations.markings, positioning}

@@

\DeclareMathAlphabet\mathbfcal{OMS}{cmsy}{b}{n}

\usepackage{algorithm, algorithmic}
